Effects of CHILDREN's programs

### 2020-02-27 paper.tex
resolved conflicts in pdf

If you want to cite \textcite{Millstein.2020} inline, use this.
If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
If you want to cite \citeauthor{Millstein.2020} only as authors, use this.

Equation with double index\\

\begin{equation}
\label{ModelProdu}
\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
\end{equation}

List\\

\begin{itemize}
  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
\end{itemize}

% Figure\\
% 
% \begin{figure}
%   \caption{Dispersion in productivity levels}
%   \label{LineDisp}
% 
% <<echo=FALSE>>=
% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
% print(figureLineDisp)
% @
% 
% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent. A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector. After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter. The shaded bars represent recessions as defined by the NBER. The year ticks refer to January 1. The dispersion measures take as their date the middle of the year, July 2. Compare Kehrig (2015), Figure 1.}
% \end{figure}

% Figure \ref{LineDisp}

% <<results='asis', echo=FALSE>>=
% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
% print(tableCyclicDisp, include.rownames = FALSE)
% @

Regression fit output with texreg\\

\begin{table}
\begin{center}
\begin{tabular}{l c c }
\hline
 & Model 1 & Model 2 \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     \\
realSubsidy      & $2.61^{***}$    &              \\
                 & $(0.57)$        &              \\
realTripsSubsidy &                 & $0.00^{*}$   \\
                 &                 & $(0.00)$     \\
\hline
R$^2$            & 0.43            & 0.05         \\
Adj. R$^2$       & 0.43            & 0.04         \\
Num. obs.        & 329             & 322          \\
RMSE             & 39992.79        & 2.96         \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Statistical models}
\label{mealsTripsSubsidyRegressions}
\end{center}
\end{table}

Table \ref{mealsTripsSubsidyRegressions}
% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
\section{Outline}
Descriptive statistics\\
dynamics of\\ 
(- number of organizations)\\
(- number of beneficiaries)\\
- selected ordinal outcomes, stacked\\
- real total subsidy\\
- real median subsidy per institution\\
- real median subsidy per beneficiary\\
(- which variables have largest variance; also relevant for variable selection)\\

Regressions\\

Questions:\\
effect of\\
- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
- real meals subsidy on number of meals\\
- real trips subsidy on number of trips\\
- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\

Methods:\\
- simple, metric\\
- standardized, metric\\
- cumulative logit\\
- with control variables\\
(- without outliers)\\
(- imputed data)\\

Diff in Diff\\

Outlook for CHILDREN/variable selection\\
- double selection \\
- partition analysis\\
(- correlation matrix)\\
(- factor analysis)\\
- general tips\\

@@

Figure\\

\begin{figure}
  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
  \label{LineDisp}

{\centering \includegraphics[width=0.8\textwidth]{figure/DaytodayskillsSelfworth-1}

\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y). The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Do, Feb 27, 2020 - 16:52:46
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{fundamentalDynamics} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
$2,011$ & $3,748$ & $$ & $52$ & $$ \\ 
$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\ 
$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\ 
$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\ 
$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\ 
$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\ 
$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\ 
$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Do, Feb 27, 2020 - 16:52:47
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{fundamentalDynamics} 
\begin{tabular}{@{\extracolsep{5pt}} c} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Summary Statistics \\ 
\hline \\[-1.8ex] 
 [1] ""                                                                                                           
 [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
 [3] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
 [4] "\\begin{table}[!htbp] \\centering "                                                                         
 [5] "  \\caption{} "                                                                                             
 [6] "  \\label{fundamentalDynamics} "                                                                            
 [7] "\\begin{tabular}{@{\\extracolsep{5pt}} ccccc} "                                                             
 [8] "\\\\[-1.8ex]\\hline "                                                                                       
 [9] "\\hline \\\\[-1.8ex] "                                                                                      
[10] "$2,011$ & $3,748$ & $$ & $52$ & $$ \\\\ "                                                                   
[11] "$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\\\ "                                                            
[12] "$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\\\ "                                                            
[13] "$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\\\ "                                                            
[14] "$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\\\ "                                                            
[15] "$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\\\ "                                                            
[16] "$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\\\ "                                                            
[17] "$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\\\ "                                                        
[18] "\\hline \\\\[-1.8ex] "                                                                                      
[19] "\\end{tabular} "                                                                                            
[20] "\\end{table} "                                                                                              
[21] ""                                                                                                           
[22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
[23] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
[24] "\\begin{table}[!htbp] \\centering "                                                                         
[25] "  \\caption{} "                                                                                             
[26] "  \\label{fundamentalDynamics} "                                                                            
[27] "\\begin{tabular}{@{\\extracolsep{5pt}} c} "                                                                 
[28] "\\\\[-1.8ex]\\hline "                                                                                       
[29] "\\hline \\\\[-1.8ex] "                                                                                      
[30] "Summary Statistics \\\\ "                                                                                   
[31] "\\hline \\\\[-1.8ex] "                                                                                      
[32] "\\end{tabular} "                                                                                            
[33] "\\end{table} "

@@

In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet. Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all, most, some, few, and none. For this figure, we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

In Figure \ref{Health_timeplots}, for the variable 'lessIll_ordered', there is much non available data (lessIll_ordered refers to the share of beneficiaries who are less frequently ill). In all years, most organizations say that most beneficiaries are more healthy. The least stated category is, that all beneficiaries are less ill. That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll_ordered', appears as good as never.

In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet. The least stated category is that some beneficiaries increased their dietary knowledge. The leftover category, few, does not appear.

The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet). Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet. The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet. The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet. The leftover category, few, also does not appear.

@@

\begin{figure}
  \caption{Selfworth and everyday expertise over time}
  \label{Equality_timeplots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth). Mostly, the answer is that most beneficiaries in most organizations have more selfworth. The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth. The leftover category, few, does not appear.

In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible. The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.

@@

\usepackage{booktabs}

@@

Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables. For these results, we use their ordinal values. The x-axis displays the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none. For example, if an organization says that most beneficiaries are healthier, then this would be coded as most. In the last reporting period, there are 13 healthy diet criteria. In previous years there were up to 15. The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not. The healthy food incex is calculated as the number of fulfilled criteria. Examples for criteria are daily carbohydrates or daily vegetables.

All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria. The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet. It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy. However, for the variable less ill, the least data is availabe. Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables. This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{Health_Plots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millenstein.2020, p.677}.

@@

\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}

How do children benefit from visiting social institutions that CHILDREN supports financially? So far this question could not be empirically validated. Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries. During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program. However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program. This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group. The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.

Empirical Approach\\

The baseline of the empirical approach is the determination of the treatment and control group. Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program. On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.

Determining the treatment and control group this way, however, was a problem.

THerefore we used the cleaned data set and only determined the control group - all organizations that have no values/answers for the questions of the Entdeckerfonds. We assume that these organizations did not receive the funding for the Entdeckerfonds and therefore are the control group in our analysis. All organizations that gave answers to at least one question of the survey part regarding the entdeckerfonds are considered the treatment group. 
Our analysis is based on this very strong definition of the treatment and control group.

Because we do not have data for the entdeckerfonds survey for the control group as this group is not observed we use the answers of the mittagstisch survey for our analysis. THerefore our possible dependent variables are limited as most of the questions are specific to the meals program.

As the dataset does not include the variables for the Entdeckerfonds survey for the control group, the potential outcomes regarding the Entdeckerfonds are not observed. Therefore we have to use the survey answers from the Mittagstisch survey.

Generally our data set contains variables from the years 2011 until 2018.

The constellation of the treatment and control group varies from year to year. 
Assumption: erhalten der treatment gleichbedeutend wie ein verlust

Possible variables as dependent variables
how we determined that:
The used variables should not be specific to the mittagstisch but more general and should also apply to the context of the Entdeckerfonds
possible variables selfworth, day to day skills
used these variables because these variables could be influenced both by the mittagstisch and entdeckerfonds and are not specific to the entdeckerfonds

looked at the general trends of these two variables with the difference of the treatment and control group to look at whether our idea makes sense

linear regression just to look at whether there are effects

add controls and fixed effects time and id fixedeffects --> explain why (id: specific effects of being in Bayern for example or the subsidy amount)
how fixed effects are implemented

which control variables we use
how we determined which controls

% \begin{table}
% \begin{center}
% \begin{tabular}{l c}
% \hline
%  & Selfworth \\
% \hline
% (Intercept)             & $-1.13^{***}$ \\
%                         & $(0.32)$      \\
% dfcEF2$treatEF          & $-0.47$       \\
%                         & $(0.31)$      \\
% \hline
% Num. obs.               & $430$         \\
% R$^2$ (full model)      & $0.47$        \\
% R$^2$ (proj model)      & $0.47$        \\
% Adj. R$^2$ (full model) & $0.36$        \\
% Adj. R$^2$ (proj model) & $0.36$        \\
% \hline
% \multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
% \end{tabular}
% \caption{linear regression}
% \label{table:coefficients}
% \end{center}
% \end{table}

Ende??
the dataset does not allow a channel analysis but these could be possible channels that might explain the effects we find

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Do, Feb 27, 2020 - 16:52:52
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

>>>>

If you want to cite \textcite{Millstein.2020} inline, use this.

If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.

If you want to cite \citeauthor{Millstein.2020} only as authors, use this.

% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}

@@

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 20:41:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccccc}
  \hline
 & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
1 & 2011 & 3748.0 &  & 52 &  \\ 
  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet. Figure \ref{HealthTimeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all, most, some, few, and none. For this figure, we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Health outcome over time}
  \label{HealthTimeplots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

In Figure \ref{HealthTimeplots}, for the variable 'lessIll\_ordered', there is much non available data (lessIll\_ordered refers to the share of beneficiaries who are less frequently ill). In all years, most organizations say that most beneficiaries are more healthy. The least stated category is, that all beneficiaries are less ill. That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll\_ordered', appears as good as never.

In the second plot of figure \ref{HealthTimeplots} (variable 'dietaryKnowledge\_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet. The least stated category is that some beneficiaries increased their dietary knowledge. The leftover category, few, does not appear.

The the bottom plot of figure \ref{HealthTimeplots}, which visualizes the variable 'appreciateHealthy\_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet). Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet. The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet. The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet. The leftover category, few, also does not appear.

@@

\begin{figure}
  \caption{Selfworth and everyday expertise over time}
  \label{EqualityTimeplots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

Figure \ref{EqualityTimeplots} shows in its upper plot the development of the answered categories for the variable selfworth\_ordered (refers to the share of beneficiaries with improved self-worth). Mostly, the answer is that most beneficiaries in most organizations have more selfworth. The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth. The leftover category, few, does not appear.

In the bottom plot of figure \ref{EqualityTimeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible. The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.

@@

@@

Figure \ref{HealthPlots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables. For these results, we use their ordinal values. The x-axis displays the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none. For example, if an organization says that most beneficiaries are healthier, then this would be coded as most. In the last reporting period, there are 13 healthy diet criteria. In previous years there were up to 15. The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not. The healthy food incex is calculated as the number of fulfilled criteria. Examples for criteria are daily carbohydrates or daily vegetables.

All plots of Figure \ref{HealthPlots} show that most organizations suffice about 5 to 10 healthy food criteria. The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet. It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy. However, for the variable less ill, the least data is availabe. Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables. This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{HealthPlots}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

@@

Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millstein.2020, p.677}.

@@

\section{The Effects of the Trips Program on Participating Beneficiaries}

How do children and adolescents benefit from visiting social institutions that CHILDREN supports financially? So far this question could not be empirically validated. Hence, one of our biggest challenges was determining a possible solution for measuring potential causal effects of the supported programs on the participating beneficiaries. During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their meals program. However, not all organizations receive additional funding to provide the trips program. This fact could be used for applying an empirical approach which determines the effects of the trips program by comparing a treatment with a control group. The aim of this analysis is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.

The basis of the empirical approach is the specification of the treatment and the control group. Using the data provided by children we determine the treatment group as all organizations that receive funding for both the trips and the meals program. On the other hand, the control group represents all organizations that only receive funding for the meals program. Therefore, the social institutions in the control group do not participate in the trips program.

\subsubsection{Specification of the Treatment Group}

When analyzing the available dataset, it was not certain which organizations actually received funding for the trips program. As previously mentioned, the CHILDREN survey consists of two parts. The first part contains questions that are specific to the meals program and the second part includes all questions which are relevant for organizations that receive funding for the trips program. The dataset shows that there are several organizations that did not provide information regarding the trips program. In consultation with Wiltrud de Haan, she informed us that these specific organizations did not receive funding to offer trips and activities. Hence, we assumed that all organizations that did not provide information regarding the trips program in a given year, did not receive funding for the program and would be part of the control group. When analyzing the possible treatment group, we realized that some organizations did not completely answer the trips program survey. There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Entdeckerfonds survey questions such as the number of trips in a given year. Wiltrud de Haan informed us, that one possible explanation for this occurrence is that these organizations did not completely use the funding in the previous year. Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the trips program with the remaining funding of the year before.

Due to these uncertainties we determine the treatment group in two different ways. Firstly, the treatment variable is specified as follows:
\begin{equation}
TreatEF_{it} =
\begin{cases}
1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
0, & \text{otherwise}
\end{cases}
\end{equation}

In this setting, once an organization receives funding for the trips program, we consider this organization as treated in the year of the first funding and all proceeding years. This implies that an organization remains in the control group as long as it does not receive funding for the trips program. Due to this definition, an organization cannot change from the treatment into the control group.

In general, the constellation of the treatment and control group varies across years. As the number of organizations supported by CHILDREN increased over time, both the treatment and control group increased as well. At first, new organizations are generally funded to provide the meals program and might receive funding for the trips program during later funding periods. In this case, organizations change from the control group into the treatment group resulting in an overall adjustment of the constellation of both groups. However, the dataset also includes organizations that switch from the treatment to the control group. The first definition of the treatment variable does not take this case into account. Therefore, we additionally construct a second treatment indicator which is defined as follows:
\begin{equation}
TreatEF_{it} =
\begin{cases}
1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape}}\\
0, & \text{otherwise}
\end{cases}
\end{equation}

Using this alternative treatment variable, the actual funding for the trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
With both definitions of the treatment variable, the number of observations units in the control group is substantially lower than in the treatment group. Consequently, the estimates cannot be very robust. Therefore, the results should not be overstated.

\subsubsection{Dependent Variables}

The fact that all organizations within the control group did not answer the trips program survey questions was helpful to categorize the control and the treatment group. However, the impact of the trips program cannot be measured with variables that are specific to the trips program as these were only observed for the treatment group. Therefore, we have to use variables of the meals program as outcome variables in our analysis. For this purpose, we identified selfworth and everyday expertise as appropriate dependent variables. Firstly, both variables are applicable to the trips program as well as the meals program. In addition, the chosen variables are observed in every year throughout the whole observation period and seem to be influenced by the fact that an organization receives funding to provide trips and other activities.

\subsubsection{Graphical Evidence}

\begin{figure}
  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
  \label{selfworth_Trend}

{\centering \includegraphics[width=0.8\textwidth]{figure/Selfworth-1}

\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to selfworth. The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}

\begin{figure}
  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
  \label{dayToDaySkills_Trend}

{\centering \includegraphics[width=0.8\textwidth]{figure/Daytodayskills-1}

\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to everyday expertise. The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}

To check for differences in treatment and control group, we created descriptive statistics regarding to the variables of interest.
Figure 5 and Figure 6 represent the development of average selfworth and average everyday expertise over time for both the treatment and control group. The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise. In the treatment group the average selfworth increased over time  while it decreased in the control group (Figure 5). Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group (Figure 6). The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents. This evidence could support the hypothesis that the trips program positively influences the beneficiaries. However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.

To check for differences in treatment and control group, we created the following graphs using descriptive statistics.

The figures represent the development of average selfworth and average everyday expertise over time for both the treatment and control group. The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise. In the treatment group the average selfworth increased over time while it decreased in the control group. Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group. The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents. This evidence could support the hypothesis that the trips program positively influences the beneficiaries. However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.

\subsubsection{Differences-in-Differences Estimation}

For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the trips program has a positive influence on the selfworth and everyday expertise of the supported children. The DID estimator measures the effect of participating in the trips program by comparing the changes in dependent variables over time between the treatment and control group. The key identifying assumption for the DID strategy is the common trend assumption. The assumption states that, in the absence of the trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same. In case of a violation of the parallel trend assumption, the estimated treatment effect would be biased. As the dataset contains 2011 as the only year in the pre-period, we are not able to observe a pre-trend. Therefore, we cannot argue that the common trend assumption is fulfilled.

Using the panel structure of the dataset we implement the DID estimation with the following regression equation:
\begin{equation}
\label{didregression}
  Y_{it} = \alpha + \beta \cdot TreatEF_{it} + \gamma_{i} + \delta_{t} + \epsilon_{it}
\end{equation}

where $i$ indexes the identification number of each organization supported by CHILDREN and $t$ indexes the year of observation. The outcome variable, denoted by $Y_{it}$, is either selfworth or everyday expertise. As mentioned in the previous section, $TreatEF_{it}$ represents the treatment status of organization $i$ in year $t$. The corresponding regression coefficient $\beta$ represents the DiD estimator, which measures the average treatment effect of participating in the trips program.

The panel data set allows us to implement fixed effects. In our analysis we introduce individual fixed effects and time fixed effects. The ID fixed effects $\gamma_{i}$ control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions. For example, the state of an organization does not vary over time but might differ across supported social institutions. Additionally, the year fixed effects $\delta_{t}$ capture all variables that change across years but are the same for all organizations and within a specific year. For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.

One concern with our empirical approach is that the allocation to treatment and control group might not be perfectly randomized because the selection into the treatment could be driven by time-variant characteristics. Therefore, we include a set of control variables to deal with potential selection bias. For this, we select variables of the available dataset that might influence both the treatment status and either of the outcome variables. Furthermore, we control for organization specific characteristics which include the subsidy received for the meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.

\subsection{Results}

\subsubsection{Everyday Expertise}
